\pagestyle{fancy}

\section{Executive Summary}
This section provides an overview of the key objectives, methodology, results, and conclusions of the project.

\section{Introduction}
\subsection{Background}
This subsection presents the context and background information relevant to the project.

\subsection{Problem Statement}
The problem statement outlines the key issues the project aims to address.

\subsection{Objectives of the Project / Project Deliverables}
This section details the main goals and deliverables of the project.

\subsection{Scope of the Project}
This section defines the boundaries and limitations of the project.

\section{Literature Review}
\subsection{Data Analytics in Avionics}
A review of relevant literature on the application of data analytics in avionics systems.

\subsection{State Estimation Techniques}
This subsection explores various state estimation methods used in aerospace applications.

\subsection{Use of Kalman Filters in Aerospace}
A discussion on the role of Kalman Filters for sensor fusion and estimation in aerospace.

\subsection{Real-Time Operating Systems (RTOS) in Avionics}
This subsection reviews the use of RTOS in avionics and its advantages for real-time task management.

\section{Methodology/Design and Justification}
\subsection{Avionics Design Overview}
An overview of the design architecture of the avionics system used in the project.

\subsection{Firmware Architecture}
This subsection describes the structure of the firmware developed for the project.

\subsection{Firmware Development}
A description of the development process for the avionics firmware, including challenges encountered.

\subsection{RTOS Implementation}
Details of the RTOS implementation and how it handles real-time task scheduling and execution.

\subsection{Data Processing and Verification Techniques}
This subsection explains the techniques used for processing and verifying sensor data.

\section{Testing and Validation}
\subsection{Sensor Testing}
An outline of the testing procedures used to validate sensor performance in the avionics system.

\subsection{RTOS Task Verification}
This subsection describes the verification process for ensuring correct execution of RTOS tasks.

\subsection{Data Logging and Retrieval}
A summary of the procedures for testing the accuracy and reliability of data logging and retrieval systems.

\subsection{Ground Communication Testing}
This subsection covers the testing of ground communication systems for real-time data transmission.

\subsection{Validation of Kalman Filter and State Estimation}
Details of how the Kalman filter and state estimation algorithms were validated under different conditions.

\section{Launch Outcomes and Results}
\subsection{Aurora I Launch Outcomes}
A summary of the results obtained from the Aurora I launch.

\subsection{Aurora II Launch Outcomes}
A summary of the results obtained from the Aurora II launch.

\subsection{Aurora III Launch Outcomes}
A summary of the results obtained from the Aurora III launch.

\subsection{Aurora IV Launch Outcomes}
A summary of the results obtained from the Aurora IV launch.

\subsection{Aurora V Launch Outcomes}
A summary of the results obtained from the Aurora V launch.

\section{Challenges}
\subsection{Time Constraints}
This subsection discusses the time-related challenges encountered during the project.

\subsection{Hardware Availability}
A description of challenges related to the availability of hardware components.

\subsection{Collaboration}
An exploration of the difficulties faced in coordinating with other teams and collaborators.

\subsection{Unexpected Code Bugs}
This subsection details unexpected software bugs encountered and how they were resolved.

\section{Conclusions and Learning Outcomes}
This section summarizes the key conclusions and lessons learned during the course of the project.

\section{Recommendations/Future Works}
\subsection{Suggested Improvements for Future Teams}
Suggestions for future teams working on similar projects to improve processes or outcomes.

\subsection{Potential Applications in Aerospace}
An overview of potential applications for the project's outcomes in other aerospace projects.

\subsection{Further Development of the Avionics System (for Spaceport)}
Recommendations for further development of the avionics system, particularly in the context of spaceport applications.

\section{References}
A list of all references used in the literature review and throughout the project.
